Effectful Semantics for Substructural SSA

### 2023-12-28 pldi24/paper.tex
Fixed typos in basic blocks with arguments, work on slides

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.33\textwidth}
    \begin{small}
    \begin{BVerbatim}[baseline=t, gobble=3]
    'entry:
      m = 0
      n = 1
      brz i 'exit 'loop
    'loop:
      t = add m n
      m = n
      n = t
      i = sub i 1
      brz i 'exit 'loop
    'exit:
      ret m
    \end{BVerbatim}
    \end{small}
    \caption{3-address code}
    \label{fig:3-addr}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \begin{small}
    \begin{BVerbatim}[baseline=t, gobble=3]
      'entry:
      m0 = 0
      n0 = 1
      brz N 
        'exit (m0) 
        'loop (i, m0, n0)
    'loop(i0, m1, n1):
      m2 = n1
      n2 = add m1 n1
      i1 = sub i0 1
      brz z1 
        'exit (m2) 
        'loop (i1, m2, n2)
    'exit(m3):
      ret m3
    \end{BVerbatim}
    \end{small}
    \caption{Basic blocks with arguments}
    \label{fig:bb-arg}
  \end{subfigure}
  \begin{subfigure}[t]{0.33\textwidth}
    \begin{small}
    \begin{BVerbatim}[baseline=t, gobble=3]
    let m0 = 0;
    let n1 = 1;
    if eq i 0 {
      br 'exit (m0)
    } else {
      br 'loop (i, m0, n0)
    } where
    'loop(i0, m1, n1) =>
      let m2 = n1;
      let n2 = add m1 n1;
      let i1 = sub i0 1;
      if eq i1 0 {
        br 'exit (m2)
      } else {
        br 'loop (i1, m2, n2)
      }
    'exit(m3) => ret m3
    \end{BVerbatim}
    \end{small}
    \caption{Our syntax}
    \label{fig:our-syn}
  \end{subfigure}
  \caption{A simple program for computing the \texttt{i}th Fibonacci number,
  represented as 3-address code, basic-blocks with arguments, and in our SSA
  syntax} 
  \Description{}
  \label{fig:ssa-examples}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.33\textwidth}
    \begin{small}
    \begin{BVerbatim}[baseline=t, gobble=3]
    'entry:
      m = 0
      n = 1
      brz i 'exit 'loop
    'loop:
      t = add m n
      m = n
      n = t
      i = sub i 1
      brz i 'exit 'loop
    'exit:
      ret m
    \end{BVerbatim}
    \end{small}
    \caption{3-address code}
    \label{fig:3-addr}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \begin{small}
    \begin{BVerbatim}[baseline=t, gobble=3]
    'entry:
      m0 = 0
      n0 = 1
      brz i
        'exit (m0) 
        'loop (i, m0, n0)
    'loop(i0, m1, n1):
      m2 = n1
      n2 = add m1 n1
      i1 = sub i0 1
      brz i1 
        'exit (m2) 
        'loop (i1, m2, n2)
    'exit(m3):
      ret m3
    \end{BVerbatim}
    \end{small}
    \caption{Basic blocks with arguments}
    \label{fig:bb-arg}
  \end{subfigure}
  \begin{subfigure}[t]{0.33\textwidth}
    \begin{small}
    \begin{BVerbatim}[baseline=t, gobble=3]
    let m0 = 0;
    let n1 = 1;
    if eq i 0 {
      br 'exit (m0)
    } else {
      br 'loop (i, m0, n0)
    } where
    'loop(i0, m1, n1) =>
      let m2 = n1;
      let n2 = add m1 n1;
      let i1 = sub i0 1;
      if eq i1 0 {
        br 'exit (m2)
      } else {
        br 'loop (i1, m2, n2)
      }
    'exit(m3) => ret m3
    \end{BVerbatim}
    \end{small}
    \caption{Our syntax}
    \label{fig:our-syn}
  \end{subfigure}
  \caption{A simple program for computing the \texttt{i}th Fibonacci number,
  represented as 3-address code, basic-blocks with arguments, and in our SSA
  syntax} 
  \Description{}
  \label{fig:ssa-examples}
\end{figure}
